### 2016-08-31 version0.0/appendixa_3.tex
Done with ch4

>>>>

\begin{figure}
\centering
\includegraphics[width=164mm]{../image_paper1/OLS_vs_bayes.png.pdf}
\caption[]{Mosaic created using the Montage programme from six fields of \halpha\ emission images of M31 from \citet{Massey07}. The resulting image from Montage was continuum-subtracted and masked for all point sources. The centre of the galaxy was masked out due to saturation of data in the continuum $R$-band image.}
\label{fig:halpha}
\end{figure}

### 2016-08-31 version0.0/intro0.01.tex
Done with ch4

\cite{Young91} described the relationship between the CO luminosity of a cloud and its mass. The CO luminosity of a cloud is:
\begin{equation}
L_{CO} = D^2 \int I_{\rm CO} d\Omega, 
\end{equation}
%NOTE: Equations must be punctuated.%
where $D$ is the distance to the cloud and $I_{\mathrm CO}$ is the CO brightness temperature integrated over the line profile in K~km~s$^{-1}$.
It can be written as ${\int T_{\mathrm CO} dV}$ where $T_{\mathrm CO}$(K) is the peak brightness temperature in the CO line and $V$ is the line-width in km~s$^{-1}$. %PB: please check this: I think \int should be omitted, dV should be \Delta V, and $V$ should also be $\Delta V$
For a uniform cloud with a radius $R$, the CO luminosity is given by:
 \begin{equation}
L_{\rm CO} = \pi R^2 T_{\rm CO} \Delta V.
\end{equation}

@@

There are disadvantages in using the gas to dust ratio to trace gas in the ISM.
In order to use the dust as a tracer of the gas mass, first a relationship between the optical depth and the mass of the dust and then a relationship between the mass of the dust and the mass of the gas must be derived.
\cite{Draine03} pointed out that the former approach is uncertain because of the uncertainly in the radiative efficiency of dust grains. 
Measuring the gas to dust ratio in galaxies are not accurate either~\citep{Hildebran83}, which means that there are problems in both steps. 
In addition, the dust method has two major practical problems: firstly, to apply this method, knowing the temperature of the dust is necessary. 
To solve this problem, measurement of the continuum emission at far-infrared wavelengths long enough to cover the peak of the emission must be very accurate~\citep{Ealas12}. 
The other problem is that there is evidence that the gas to dust ratio depends on the metallicity of the gas~\citep{Lisenfeld98, Draine07}, but even in direct methods the dependence on metallicity must be solved. 
Using dust emission as a tracer of gas is the best alternative for measuring the total gas in galaxies, that there is no observation of CO or \hi~emission.

\subsection{The ISM and starlight: extinction and attenuation}
\label{sec: extinction}
Dust in ISM affects stellar emission by attenuating, scattering or absorption.
Effect of dust clouds with embedded light sources on distribution of the light is called attenuation. 
The dust cloud could have any distribution and be clumpy or smooth. 
Since both light source and dust have extended distributions, the relative locations of the dust and light source affect the net absorbed and scattered light.
The other parameter that is important for the scattering and absorption is the relative position of dust and observer.
When the dust is in the line of sight, attenuation will make the emerging light dimmer~\citep[e.g.][and references therein]{Calzetti13}.
This is the typically occurring situation when studying galaxies or extended regions within galaxies.

>>>>

\cite{Young91} described the relationship between the CO luminosity of a cloud and its mass. The CO luminosity of a cloud is:
\begin{equation}
L_{CO} = D^2 \int I_{\rm CO} d\Omega, 
\end{equation}
%NOTE: Equations must be punctuated.%
where $D$ is the distance to the cloud and $I_{\mathrm CO}$ is the CO brightness temperature integrated over the line profile in K~km~s$^{-1}$.
It can be written as ${\int T_{\mathrm CO} dV}$ where $T_{\mathrm CO}$(K) is the peak brightness temperature in the CO line and $V$ is the line-width in km~s$^{-1}$. %PB: please check this: I think \int should be omitted, dV should be \Delta V, and $V$ in text should also be $\Delta V$
For a uniform cloud with a radius $R$, the CO luminosity is given by:
 \begin{equation}
L_{\rm CO} = \pi R^2 T_{\rm CO} \Delta V.
\end{equation}

@@

There are disadvantages in using the gas to dust ratio to trace gas in the ISM.
In order to use the dust as a tracer of the gas mass, first a relationship between the optical depth and the mass of the dust and then a relationship between the mass of the dust and the mass of the gas must be derived.
\cite{Draine03} pointed out that the former approach is uncertain because of the uncertainly in the radiative efficiency of dust grains. 
Measuring the gas to dust ratio in galaxies are not accurate either~\citep{Hildebran83}, which means that there are problems in both steps. 
In addition, the dust method has two major practical problems: firstly, to apply this method, knowing the temperature of the dust is necessary. 
To solve this problem, measurement of the continuum emission at far-infrared wavelengths long enough to cover the peak of the emission must be very accurate~\citep{Ealas12}. 
The other problem is that there is evidence that the gas to dust ratio depends on the metallicity of the gas~\citep{Lisenfeld98, Draine07}, but even in direct methods the dependence on metallicity must be solved. 
Using dust emission as a tracer of gas is the best alternative for measuring the total gas in galaxies where there are no observations of CO or \hi~emission.

\subsection{The ISM and starlight: extinction and attenuation}
\label{sec: extinction}
Dust in ISM affects stellar emission by attenuating, scattering or absorption.
The effect of dust clouds with embedded light sources on the distribution of the light is called attenuation. 
The dust cloud could have any distribution and be clumpy or smooth. 
Since both light source and dust have extended distributions, the relative locations of the dust and light source affect the net absorbed and scattered light.
The other parameter that is important for the scattering and absorption is the relative position of dust and observer.
When the dust is in the line of sight, attenuation will make the emerging light dimmer~\citep[e.g.][and references therein]{Calzetti13}.
This is the typically occurring situation when studying galaxies or extended regions within galaxies.

### 2016-08-31 version0.0/paper2.tex
Done with ch4

 \subsection{Kinney Spectral Model}
     \begin{figure}
        \centering
        \includegraphics[width=0.9\textwidth]{../image_paper2/k96.jpg}
        \caption[\citet{Kinney96} spectral templates for 12 types of galaxies]{\citet{Kinney96} spectral templates for 12 types of galaxies from \citet{Hossein12} paper (Fig. 1 in \citet{Hossein12}). The type of each template is shown in each frame. Plots B, E, S0, Sa, Sb and SC show spectra that belong to quiescent galaxies. Starburst galaxy spectra are indicated with SB 1 to 6. Higher numbers represent more intrinsic extinction.}
        \label{fig: k96}
    \end{figure}

>>>>

 \subsection{Kinney Spectral Model}
     \begin{figure}
        \centering
        \includegraphics[width=0.9\textwidth]{../image_paper2/k96.jpg}
        \caption[\citet{Kinney96} spectral templates for 12 types of galaxies]{\citet{Kinney96} spectral templates for 12 types of galaxies from Fig. 1 in \citet{Hossein12}. The type of each template is shown in each frame. Plots B, E, S0, Sa, Sb and SC show spectra that belong to quiescent galaxies. Starburst galaxy spectra are indicated with SB 1 to 6. Higher numbers represent more intrinsic extinction. Note that he vertical axis label from \citet{Hossein12} is incorrect: the quantity plotted is flux density, not flux.}
        \label{fig: k96}
    \end{figure}
